---
title: "PCTG R Markdown template"
author: "[Arnaud Frering](https://github.com/ArnaudFrering)"
date: "`r format(Sys.time(), '%d %B %Y')`"
mail: "arnaud.frering@mines-ales.org"
linkedin: "arnaud-frering-b52150161"
github: "ArnaudFrering"
output:
  epuRate::PCTG:
    toc: TRUE
    number_sections: FALSE
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# You need these libraries to run this template:
library(rmarkdown)    # install.packages("rmarkdown") 
library(epuRate)      # devtools::install_github("holtzy/epuRate", force=TRUE)
```
# Basic dataviz with R and ggplot2

This practical will teach you the basics of ggplot2. It is split in 4 parts, each dedicated to a chart family:

*Correlation: scatterplot and bubble plot  
*Distribution: histogram, density and boxplot.  
*Ranking: barplot, lollipop and treemap.  
*Evolution: line plot and area chart  

```{r cars, echo=FALSE}
library(ggplot2) 
library(dplyr)
library(gapminder) 
library(hrbrthemes)
```

## Question 1.1
Load the gapminder dataset stored in the gapminder package. Have a look to the 6 first rows using the head() function. Describe briefly what you see as comments in your script. Check how many rows are available with nrow()

```{r,}
head(gapminder)

nrow(gapminder)
```

## Question 1.2
How many years are available in this dataset? How many data-points for each year? Full code is provided for this question.

```{r,}
gapminder %>%
  select(year) %>%
  unique() %>%
  nrow()
```

```{r,}
gapminder %>%
  group_by(year) %>%
  summarize( n=n() )
```

## Question 1.3
Build a scatterplot showing the relationship between gdpPercap and lifeExp in 1952. Use geom_point(). What do you observe?

```{r,}
gapminder %>%
  filter(year=="1952") %>%
  ggplot( aes(x=gdpPercap, y=lifeExp)) +
  geom_point(color = "green")
```

## Question 1.4
On the previous chart, one country is very different. Which one is it?

```{r,}
gapminder %>%
  filter(year =="1952" & gdpPercap>60000) 
```

```{r,}
library(DT) 
datatable(mtcars, rownames = FALSE, filter="top", options = list(pageLength = 5, scrollX=T))
```


